### 2019-07-01 report/chapter03.tex
correction of tes

\chapter{Results}

% 
% \section{Meta-analysis}
% The data at hand is composed of over 400,000 results with balanced sample size $n > 24$. The significance of the p-values of treatment effect estimates was calculated for all results in the dataset with acceptable sample size and outcome measures as odds ratios, peto odds ratios, risk ratios, risk differences and mean and standardized mean differences. 
% 
% %Significance over time? Chunck 1
% 
% The results that can be pooled are analysed by fixed-effects meta-analysis, random-effects meta-analysis and random-effects meta-analysis with Hartung-Knapp method.
% 
% \vspace{0mm}
% In the following, the results are combined with the results of their corresponding meta-analysis if possible (i.e. if studies were not unique in the dataset with respect to their experimental setup). The significance of the treatment effect (primary significance) in a single result is then compared to the significance of the pooled treatment effect (secondary significance). 
% In Figure \ref{primary.secondary.significance}, the overall fraction of studies with significant and non-significant meta-analysis results is shown. The meta-analysis method used to pool the treatment effect estimates and assessing significance is indicated on the right hand side of the Figure. The colors indicate the overall fraction of rejected or accepted null-hypotheses of no treatment effect.
% 
% \begin{figure}
% <<echo=FALSE, warning=FALSE>>=
% #plot(sig.meta.c)
% @
% \caption{Overall fraction of studies whose treatment effect estimate was significant when pooled by means of meta-analysis. The fractions have been calculated
% by fixed-effects, random-effects and Hartung and Knapp adjusted random-effects meta-analysis}
% \label{primary.secondary.significance}
% \end{figure}
% 
% What has been found is that even the meta-analysis that for all meta-analysis methods, the amount of secondary significance is higher than the amount of primary significance. Thus more primarily non-significant results can be attached to a secondarily significant result than vice-versa.
% 
% \vspace{0mm}
% To illustrate this, the fraction of studies with significant primary treatment effect and primary non-significant treatment effect can be plotted separately (Figure \ref{primary.secondary.significance.sep.sig}). 
% 
% \begin{figure}
% <<echo=FALSE, warning=FALSE>>=
% #grid.arrange(sig.meta.plot1, nonsig.meta.plot, ncol= 1)
% @
% \caption{Overall fraction of studies whose treatment effect estimate was significant when pooled by means of meta-analysis, separated by significance of study treatment effect estimate. The fractions have been calculated
% by fixed-effects, random-effects and Hartung and Knapp adjusted random-effects meta-analysis}
% \label{primary.secondary.significance}
% \end{figure}
% 
% It can be seen that the extent of overlap between primary and secondary significance varies between meta-analysis. A considerable amount of both primary significant and primary non-significant results are overruled by meta-analysis hypothesis tests. 
% 
% 
% The amount of significant heterogeneity in the results used by the meta-analyses is length(which(mly$sig.Q == 0)) and corresponds to (length(which(mly$sig.Q == 0))/ dim(mly)[1])*100\% of the total number of meta-analyses.
% 
% %Comparison of significance separated for significant Q? Chunck 2
% 
% %Proportion of significant pooled estimates based on proportion of single pooled estimates? Chunck 5

\section{Small study effects}

To provide an overview over the abundance of small study effects in the dataset, first it is shown how median absolute effect size decreases with increasing sample size of the results (Figure \ref{effect.samplesize}). 
%In some sense, this is the same idea as for a funnel plot, by depicting the size of effects relative to their variance.

\vspace{0mm}
A clear trend of decrease of absolute effect size with increasing sample size (i.e. smaller variance) is visible. 
%It is particularly substantive from very small trials ($n$ = 10) to medium sample size ($n$ = 100) and afterwards it evens off. With increasing sample size, there are fewer results, therefore, the variation between medians increases. 
All effects are normalized by subtracting the mean effect size of the dataset and dividing through the standard deviation. Note that various types of outcome measures are included, such as mean difference and risk ratios, and are normalized with respect to all effects.

@@

{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-5-1}

@@

\end{knitrout}
\caption{Median of the absolute value of the normalized effect size plotted against the total sample size.}
\label{effect.samplesize}
\end{figure}

The median absolute normalized effect size can be visualized for the different outcome measures separately (Figure \ref{effect.samplesize.separated}). The plot confirms the trend of median effect size decrease towards lower sample size (e.g. for Risk Ratios: decrease $> 0.1$ standard deviations from 10 to 50 study participants). Instead of normalizing the effects 
%(i.e. subtracting mean and dividing through the standard deviation) 
for all effect sizes, the effects are normalized with respect to the effects of the same outcome measures.

@@

{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-6-1}

@@

\end{knitrout}
\caption{Median of the absolute value of the normalized effect size plotted against the total sample size, separated for outcome measures.}
\label{effect.samplesize.separated}
\end{figure}

%Show absolute effect size depending on scaled time? Chunck 3

\subsection{Small Study Effect Tests}

There are tests that can be applied to find out if small study effects are present in the meta analysis. For the precise description, see the methods section. Application of the tests is only recommended if there are ten or more studies \citep{cochrane.handbook} that can be used, so all meta-analyses with less than ten studies have been excluded.

\vspace{0mm}
There are modifications to make tests more appropriate in case of binary outcomes, therefore the results have been separated in continuous and dichotomous outcome test results. In Figure \ref{bias.results.cont} the proportion of test results that led to rejection of the null hypothesis of no small study effect based on the 5 \% level are shown for continuous outcomes ($n$ = 1383)
The same is shown in Figure \ref{bias.results.bin} for dichotomous outcome measures ($n$ = 3955). The amount of studies varies from 5\% (Schwarzer's Test) to 13 \% (Egger's Test) for binary outcomes and 9\% (Begg and Mazumdar's Test) to 25 \% (Egger's Test) for continuous outcomes.

@@

{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-8-1}

@@

\end{knitrout}
\caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (continuous outcomes).}
\label{bias.results.cont}
\end{figure}

@@

{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-9-1}

@@

\end{knitrout}
\caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (dichotomous outcomes).}
\label{bias.results.bin}
\end{figure}

There is no substantive change in the fraction of positive test results, depending on if the pooled treatment effect size estimate is significant or not. Most substantively, the fraction of positive Egger Test results increases for significant pooled treatment effects by 0.1825716 (the minimal increase is -0.0032246 for Schwarzer's Test).

%Show plots of significant meta-analyses separated? Chunck 4

Furthermore one can look if the frequencies of tests that reject the null hypotheses change over time (mean publication year of the studies included in the meta analyses). The proportion of the test results are shown in Figure \ref{pub.bias.time.overtime}. The Figure suggests that the frequency of publication bias remains constant over time. The mean publication years have been restricted such that at least 180 meta-analyses are available per year, such that random fluctuation is restricted to some extent. The significance threshold for the $p$-values used is 0.05, and the small study effect test used is Thomson's test (with the arcsine variance stabilizing transformation function used in the case of binary outcomes).

@@

{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-10-1}

@@

\end{knitrout}
\caption{Proportion of test results where the null hypothesis of no small study effect is rejected over time (mean publication.year).}
\label{pub.bias.overtime}
\end{figure}

The agreement of the tests, i.e. the proportion of meta-analyses where the rest results are equal between tests, is shown in Table \ref{agreement.bin} and Table \ref{agreement.cont}, again separated for outcome types. Agreement in tests for binary outcomes is better than continuous outcomes, with some variation between tests (binary outcomes: 83 to 91\%). Correlation varies more between tests, both for continuous and binary outcome tests.

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Tue May 21 16:11:40 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lll}
  \hline
 & Test Agreement & P-value Correlation \\ 
  \hline
egger.schwarzer & 0.73 & 0.23 \\ 
  egger.peter & 0.75 & 0.37 \\ 
  egger.rucker & 0.75 & 0.34 \\ 
  egger.harbord & 0.79 & 0.51 \\ 
  schwarzer.peter & 0.81 & 0.26 \\ 
  schwarzer.rucker & 0.81 & 0.25 \\ 
  schwarzer.harbord & 0.86 & 0.47 \\ 
  rucker.peter & 0.87 & 0.64 \\ 
  harbord.peter & 0.84 & 0.50 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Proportion of tests that agree in rejection ar acceptance of the null hypothesis that there is no small study effect (dichotomous outcomes)} 
\label{agreement.bin}
\end{table}

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Tue May 21 16:11:40 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lll}
  \hline
 & Test Agreement & P-value Correlation \\ 
  \hline
thomson.egger & 0.85 & 0.69 \\ 
  thomson.begg & 0.77 & 0.47 \\ 
  egger.begg & 0.73 & 0.36 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Proportion of tests that agree in rejection ar acceptance of the null hypothesis that there is no small study effect (continuous outcomes)} 
\label{agreement.cont}
\end{table}

\vspace{0mm}
Test performance depends on the sample size, despite having restricted sample size to a minimum of 10 studies. The p-values of the Thompson and Sharp tests are shown with respect to the sample size of the meta-analysis in Figure \ref{pvalues.samplesize}. %(Suggests that 10 is likely too small)
In the case of binary outcomes, the arcsine variance stabilizing function has been applied prior to use of Thompson and Sharp's test. A trend towards more rejections for larger sample sizes can be seen.

@@

{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-13-1}

@@

\end{knitrout}
\caption{P-values of Thomson and Sharp's test for small study effects and their corresponding sample size.}
\label{pvalues.samplesize}
\end{figure}

\vspace{0mm}
One can use the proportion of added studies by the trim-and-fill method from the overall number of studies to further investigate the extent of small study effects. The mean fraction of trimmed comparisons for binary outcomes is 0.19 and the median 0.18. 
% A histogram with those fractions is shown in Figure \ref{trimfill.cont} for continuous outcomes and \ref{trimfill.bin} for dichotomous outcomes. In both cases, the method very commonly adds supposedly unpublished studies to the meta-analyses. 
In Figure \ref{trimfill.pvalues.bin} and Figure \ref{trimfill.pvalues.cont}, the relationship between fraction of added studies by trim-and-fill and the hypothesis test decisions of the small study effects tests is shown for continuous and dichotomous outcomes. In the case of Peters test dor dichotomous outcomes, there is less agreement with the trim-and fill method than in the case of Thomson and Sharp's test for continuos outcomes in the sense that the fraction of meta-analyses with rejected null hypothesises increases more clearly when there are more studies added by trim-and-fill.

>>>>

\chapter{Results} \label{ch:Results}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Small Study Effect and Excess of Significance Tests} \label{sec:publication.bias.tests}

The meta-analyses fulfilling the criteria from chapter \ref{ch:dataset}, section \ref{sec:Processing}, are analysed with small study effects tests and excess significance tests. We will apply the tests on the original effect size measures, i.e. risk ratios, Hedges $g$ or log hazard ratios. Different tests are applied depending on if the outcomes are of type binary or continuous or survival.\\
Thus, we apply multiple tests on the same data. The results can then be displayed separately to compare the different tests. A histogram of $p$-values will summarize the overall evidence against the null-hypothesis of no publication bias, as displayed in Figure \ref{fig:test}. \\
``Excess significance'' denotes the excess of significant $p$-values testing method from \citet{excess.significance}, see \ref{sec:excess.significance}. For continuous and survival outcomes, the names refer to:

\begin{itemize}
\item Egger's test, the weighted linear regression test as described in section \ref{sec:Egger}
\item Thompson and Sharp's test, the weighted linear regression test adjusted for between-study heterogeneity, section \ref{sec:Thompson}
\item Begg and Mazumdar's test, the rank test described in section \ref{sec:Begg}
\end{itemize}

For binary outcomes, the names refer to:
\begin{itemize}
\item Harbord's test, the likelihood score based test (section \ref{sec:Harbord})
\item Peter's test, the weighted linear regression with inverse sample size as explanatory variable (study size proxy) described in section \ref{sec:Peter}
\item R\"ucker's test, the test based on the arcsine transformation of proportions, in combination with Thompson and Sharp's regression test (section \ref{sec:Rucker})
\item Schwarzer's test, the rank based test using the expected event counts computed with the hypergeometric distribution (section \ref{sec:Schwarzer})
\end{itemize}

@@

{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-2-1}

@@

\end{knitrout}
\caption{Histogram of the $p$-values for small study effect in meta-analyses. The testing method is indicated in the header, bin width is equal to 0.1. The significant proportion based on the threshold of 0.1 is displayed inside the figures.}
\label{fig:test}
\end{figure}

%Agreement table -> Chunck 1
The histograms in Figure \ref{fig:test} show that the distributions are (with the exception of Schwarzer's test) skewed to the right for all outcome types, indicating evidence for small study effects and excess significance, respectively. Moreover, the excess significance tests have a mode around $p = 0.4$. There is some discrepancy between continuous and binary data test results; the evidence for small study effects in continuous data is clearly larger. Survival outcome type results are quite different with very few evidence for small study effects, but almost 50\% of meta-analysis with significant excess significance tests. Note that the sample size of survival outcomes is small ($n$ = 39).\\
It cannot be seen in Figure \ref{fig:test} if the tests used are finding small study effects/excess significance for the same meta-analyses. A simple method to check the coincidence of test results is to compare scatterplots and empirical Spearman correlations between the test statistics. This is done in Figure \ref{fig:test.agreement}. Here, there is no separation between survival and continuous outcomes. The upper left rectangle is displaying binary outcome results and the lower right continuous and survival outcomes results.

@@

{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-3-1}

@@

\end{knitrout}
\caption{Pairs-plot for test statistics of small study effect and excess significance. The lower panel gives the Spearman correlations for the different test statistics, and the upper panel displays a scatterplot. The colors indicate magnitude and direction of the correlation coefficients. The rectangle with white borders displays the area within which both tests have absolute value < 1.64 (dots outside are statistically significant using the 0.1 threshold).}
\label{fig:test.agreement}
\end{figure}

The observed patterns on the scatterplots differ: Excess significance and small study effect test statistics do usually not align with each other, forming rather randomly scattered bulks of points. Regression based tests as Egger and Thompson which are methodically almost identical are closely aligned, which is reflected in large correlation coefficients. In general, small study effect tests align on the diagonal, but the extent to which they align differs. Continuous and survival outcome type tests align more closely than binary outcome tests. While correlation coefficients between binary outcome tests vary between each other, Harbord's test statistic has similar correlation coefficients with the other small study effect test statistics .\\
Because scatterplots and correlation coefficients can be misleading, also a Tukey mean-difference or Bland-Altman of transformed $p$-values plot is shown for four scenarios in Figure \ref{fig:mean.diff.test}:
\begin{itemize}
\item For Egger's and Thompson's tests, which is supposedly the most similar test and should show the least deviations and systematic errors
\item For Egger's and excess significance tests
\item For Harbord's and R\"ucker's tests
\item For Harbord's and excess significance tests
\end{itemize}

This can be justified since all tests are supposed to measure the evidence for publication bias. For the plots, the $p$-values of the tests are transformed on the entire continuous scale by a logit transformation $f(x)  = \log\frac{p}{1-p}$). The mean $p$-value (($f$($p$-value no. 1) + $f$($p$-value no. 2))/2) is then displayed against the difference between the $f$($p$-value). If no systematic errors and biases exist between the measurement methods, then

\begin{itemize}
\item the mean of the differences should be around zero (systematic error) 
\item the points should scatter independently on the $y$-axis and no general increase or decrease with the mean of the transformed $p$-values should be visible
\end{itemize}

Although this is not formally tested, the last criterium seems not to be given when comparing small study effect and excess significance tests. With decreasing mean, the difference gets more negative, and vice versa, such that one would predict that the excess significance $p$-values are more ``extreme'' in both directions. -- In the appendix, it can be seen that this is reproducible with the remaining small study effect tests (not there yet) -- However, the systematic error between the compared tests is close to zero, and small study effect tests do probably not show bias when compared to each other. \\
The confidence intervals can be used as limits of agreement, which gives, after back-transformation, around 0.9 for Egger's and Thompson's test, and around 0.99 for Harbord's and R\"ucker's tests. This suggests that correspondence between the tests is not very good in general.

@@

{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-4-1}

@@

\end{knitrout}
\caption{Mean - difference plots for logit transformed $p$-values. The mean of logit transformed $p$-values is displayed on the $x$-axis and the difference on the $y$-axis. Blue and red lines display the systematic error and the confidence intervals of the systematic error (limits of agreement).}
\label{fig:mean.diff.test}
\end{figure}

The previous results suggest that the results will also differ substantially after applying the common dichotomization of $p$-values. We expect that some proportion of the meta-analysis will only be significant for a certain test, and this is indeed observed in Table \ref{number.sig.tests}. It displays the percentage of meta-analyses with a certain number of significant test results.

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Mon Jul  1 14:05:10 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{ccc}
  \hline
Count & Binary Outcomes & Continuous and Survival \\ 
  \hline
0 & 65.1 \% & 70.4 \% \\ 
  1 & 16.8 \% & 9 \% \\ 
  2 & 8.8 \% & 7.5 \% \\ 
  3 & 5.9 \% & 10.8 \% \\ 
  4 & 3.1 \% & 2.3 \% \\ 
  5 & 0.4 \% & - \\ 
   \hline
\end{tabular}
\endgroup
\caption{Counts Number of significant test results per meta-analysis, separated
       for outcome types. Last entry for continuous and survival outcomes is empty since one test less was 
       applied} 
\label{number.sig.tests}
\end{table}

Here, it is difficult to say if continuous and survival or binary outcome types show better agreement, since more tests are applied in the binary case, and the continuous and survival outcome type tests have in general more positive findings. Very few meta-analyses are significant, irrespective of the test used, but around 67\% of the dataset is not significant, no matter which test is used. \\
When only looking at small study effect tests, 29.1\% of binary outcome tests and 26.2\% of survival and continuous outcome tests had at least one significant result. This also suggests that the overlap between small study effect tests and excess significance is small. After applying the Bonferroni correction for multiple testing, this shrinks to 10.9\% for binary and 12.1\% for continuous and survival outcomes. \\
To compare significant findings for small study effect tests and excess significance tests, we limit ourselves to comparison with Harbord's or Egger's test. 23.5\% of binary outcome analyses had at least one of the two test $p$-values being significant, and equivalently, 25.4\% for continuous and survival outcomes. The numbers change to 14\% for binary outcomes and 14.4\% for continuous and survival outcomes after applying the Bonferroni correction. \\
3.2\% have significant Harbord's test result and significant excess significance test result  (1.1\% with Bonferroni). Of the continuous outcomes, we have 5.7\% with Egger's test and 1.8\% with Bonferroni correction.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Small Study Effects Adjustment}

\subsection{Change in Effect Size after Adjustment} \label{sec:change.size}

Since there's evidence for publication bias when applying small study effect and excess significance tests, we apply small study effect adjustment methods to correct for small study effect tests. \\
We will see that consequences of adjustment can be; 
\begin{itemize}
\item first, the absolute size of the treatment effect can be smaller than the classical meta-analysis treatment effect, which is expected if publication bias
is the cause for the small study effect.
\item secondly, the effect can be larger than before in meta-analysis. In this case, the small study effect must be not due to publication bias for large effects (``true'' publication bias), but due to bias for small effects (``negative publication bias'').
\end{itemize}

In section \ref{sec:comparison.tests.adjustment}, it will be followed up on the latter point. For now, we will examine the extent and the frequencies of the two scenarios. \\
To compare the effects of adjustment between meta-analyses, the outcome measures are transformed to Hedges $g$ (standardized mean differences) and Fisher's $z$-score (see section \ref{sec:transformation.effectsizes} for details). The effect of adjustment can additionally be compared to either random or fixed effects meta-analysis. \\
Figure \ref{fig:adjustment.size} displays the difference $\delta$ between the observed meta-analysis pooled treatment effect and the adjusted treatment effect, $\hat{\theta}_M - \hat{\theta}_\textrm{Adj.}$. The absolute value $|\hat{\theta}_M|$ is taken and the sign of $\hat{\theta}_\textrm{Adj.}$ is adjusted accordingly such that all effects are mirrored to one side. $\delta > 0$ is equivalent to $\hat{\theta}_\textrm{Adj} < \hat{\theta}_M$, a reduction of the original effect size. For better illustration, some very large and very small differences have been omitted in the $z$-score and Hedges $g$ histograms; they are shown in Table \ref{missing.differences}. Table \ref{adjustment.difference} shows the quantiles and means for the various differences and additional information.\\

@@

{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-7-1}

@@

\end{knitrout}
\caption{Histogram of the treatment effect differences between meta-analysis and adjusted meta-analysis. Negative differences indicate greater adjusted effect sizes than meta-analysis effect sizes. The bins are centered at zero.}
\label{fig:adjustment.size}
\end{figure}

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Mon Jul  1 14:05:13 2019
\begin{table}[ht]
\centering
\begingroup\scriptsize
\begin{tabular}{lcccccccccr}
  \hline
 & 5\% & 25\% & 50\% & 75\% & 95\% & mean & = 0 (\%) & $>$= 0 (\%) & $>$ 0 (\%) & No adj. est. (\%) \\ 
  \hline
z: Fixed - Copas & -0.05 & -0.01 & -0.00 & 0.01 & 0.05 & -271.73 & 4.76 & 48.67 & 43.91 & 71.54 \\ 
  z: Random - Copas & -0.00 & 0.00 & 0.00 & 0.00 & 0.04 & -263.62 & 71.65 & 89.42 & 17.77 & 71.54 \\ 
  z: Fixed - Regression & -0.13 & -0.03 & 0.01 & 0.05 & 0.14 & 0.01 & 0.00 & 52.44 & 52.44 & 0.17 \\ 
  z: Random - Regression & -0.15 & -0.03 & 0.02 & 0.07 & 0.18 & 0.02 & 0.00 & 57.64 & 57.64 & 0.17 \\ 
  g: Fixed - Copas & -0.05 & -0.01 & 0.00 & 0.01 & 0.09 & 0.02 & 22.76 & 59.14 & 36.38 & 60.96 \\ 
  g: Random - Copas & -0.00 & 0.00 & 0.00 & 0.00 & 0.14 & 0.03 & 63.29 & 87.49 & 24.20 & 60.96 \\ 
  g: Fixed - Regression & -0.23 & -0.04 & 0.03 & 0.13 & 0.38 & 0.05 & 0.00 & 61.96 & 61.96 & 0.00 \\ 
  g: Random - Regression & -0.24 & -0.03 & 0.05 & 0.16 & 0.42 & 0.06 & 0.00 & 64.06 & 64.06 & 0.00 \\ 
  Log h.r.: Fixed - Copas & -0.03 & 0.00 & 0.00 & 0.00 & 0.02 & -0.01 & 41.03 & 38.46 & 79.49 & 61.54 \\ 
  Log h.r.: Random - Copas & -0.03 & 0.00 & 0.00 & 0.00 & 0.00 & -0.01 & 66.67 & 15.38 & 82.05 & 61.54 \\ 
  Log h.r.: Fixed - Regression & -0.21 & -0.14 & -0.07 & 0.01 & 0.15 & -0.06 & 0.00 & 33.33 & 33.33 & 0.00 \\ 
  Log h.r.: Random - Regression & -0.22 & -0.15 & -0.07 & 0.03 & 0.15 & -0.06 & 0.00 & 33.33 & 33.33 & 0.00 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Quantiles and Means of the differences between meta-analysis pooled treatment effects and small study adjusted treatment effects. The column with the names ``> 0'' give the percentages of estimates larger than zero or larger or equal zero. The column ``No adj. est.'' gives the percentage of missing estimates due to non-significant publication bias test (for Copas) and computational errors. The row names indicate which outcome measure, meta-analysis method and adjustment method is used. Abbreviations are used for z-score (= z) and Hedges g (= g).} 
\label{adjustment.difference}
\end{table}

Adjustment leads most often to reduction of treatment effect estimates, as can be seen by the size of the bins of the right part of the histograms in Figure \ref{fig:adjustment.sue}. The difference between the bins on the right and left side of the zero-centered bin is however not very large in general. The seeming exception of the Copas selection model in the case with $z$-scores and fixed effects reference requires closer examination: Copas selection model substitutes its estimates with random effect estimates when it finds no evidence for small study effects. Thus, when comparing Copas with Fixed effects, we compare most often random effects with fixed effects estimates. The effect of adjustment by Copas can therefore only be seen when comparing random effects estimates with fixed effect estimates: we can see in Table \ref{adjustment.difference} that we have, for $z$-score, 18.4\% reduced effect sizes compared to 10.3\% (= 100\% - 89.69\%) increased effect sizes. Thus, the Copas selection model also has a larger proportion of reduced effect sizes compared to amplified.\\
%This resolves the case for the seeming exception and for Hedges $g$'s, 24.4\% and 12.46\% (Table \ref{adjustment.difference}. 
Also, there are more reduced effect sizes if random effects meta-analysis is used as a reference effect size. When Hedge's $g$ is used as an effect measure, there are (substantially) more reduced effect sizes. \\
The means in Table \ref{adjustment.difference} suggest that the average reduction is small (the means of Copas in the first two rows for $z$-score are caused by one very large value, see Table \ref{missing.differences}). To recall some other findings out of Table \ref{adjustment.difference}: 5\% or 90 cases have their $z$-score reduced by more than 0.15 by regression adjustment (and 5\% or 90 increased by -0.13, fixed effects reference). Also, Hedges $g$ is reduced by 0.39 compared to fixed effects estimates in 5\% or 90 meta-analyses (or increased by 0.24).

\subsection{Change in Evidence for Treatment Effects} \label{sec:change.evidence}
Adjustment for small study effects in meta-analysis will not only provide new effect sizes, but also standard errors thereof. Thus, also the evidence for efficacy of a treatment can be obtained, which is usually summarized in a suitable test statistic or $p$-value. It is of interest if and how the evidence for treatment effects changes if adjusted for publication bias.\\
The Wald test statistics $p$-value for fixed and random effects meta-analyses and Copas and regression adjusted treatment effects have been calculated. They are shown in Figure \ref{fig:adjustment.stat} for meta-analysis based on $z$-score, Hedges $g$ and log hazard ratios. \\
It can be seen that evidence for a treatment effect decreases after adjusting for publication bias. It does so more for Hedge's $g$ compared to $z$-scores, and for regression adjustment compared to Copas selection model. 
%Also, the evidence decreases for random effects meta-analyses compared to fixed effects meta-analyses. 
In the case of log-hazard ratio adjustment, the adjustment has only negligible impact on the $p$-values. \\
Also, Copas selection method has a very small impact on the evidence compared to random effects meta-analysis, at least using $z$-scores (again, we should rely on comparisons to random effects meta-analysis to evaluate Copas method). \\ 
% Interestingly, in contrast to the small study effect tests, there seems to be no large difference between adjusted continuous and binary meta-analysis test statistics --appendix--
%Figures \ref{fig:adjustment.stat.z} for the adjusted $z$-scores, \ref{fig:adjustment.stat.smd} for the adjusted Hedges $g$ and Cohen's d and \ref{fig:adjustment.stat.log.hazard.ratio} for the adjusted log hazard ratios.

@@

{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-9-1}

@@

\end{knitrout}
\caption{Histogram of the Wald test-statistic $p$-value of meta-analysis and adjusted pooled treatment effect, based on different treatment effect measures. The method is indicated in the header, bin width is set to 0.05. The significant proportion based on the threshold of 0.05 is displayed inside the figures.}
\label{fig:adjustment.stat}
\end{figure}

The Copas selection model also gives an estimate of the number of missing studies. It finds that 0 are missing, which corresponds to 0\% from all \ensuremath{2.8945\times 10^{4}} analysed studies. Figure \ref{fig:copas.missing} shows a histogram of the overall fraction of missing studies. Note that we have excluded 0 out of 1806, for which no Copas selection model estimate, but a random effects estimate was retained because the algorithm initially found no evidence for small study effects.

@@

{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-10-1}

@@

\end{knitrout}
\caption{Histogram of the fraction of missing studies from the total number of studies in a meta-analyses (only data shown where Copas estimate was obtained, thus \\$n =$ 0)}
\label{fig:copas.missing}
\end{figure}

We can see that in some occasions, the method finds more than half of all studies are missing. In most occasions, the estimate of missing studies is zero, as can be seen in Table \ref{copas.missing}. The discrepancy between mean and median may indicate that the estimate of 0\% missing studies depends somewhat on these extreme cases. As can be written of from Table \ref{copas.missing}, 5\%, \ie 0 meta-analyses have 17.6 or more studies missing: in fact, these 5\% most extreme make up for 0, more than 30\% of missing studies.

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Mon Jul  1 14:05:15 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lrrrrrrr}
  \hline
 & = 0 & 5\% & 25\% & 50\% & 75\% & 95\% & mean \\ 
  \hline
Missing fraction & 321 & 0 & 0 & 0.1 & 0.3 & 0.9 & 0.2 \\ 
  Missing study number & 321 & 0 & 0 & 1.4 & 5.2 & 17.6 & 4.1 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Fraction of missing studies and estimates of missing studies with their zero counts (``= 0''), quantiles and means.} 
\label{copas.missing}
\end{table}

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Mon Jul  1 14:05:15 2019
\begin{table}[ht]
\centering
\begingroup\tiny
\begin{tabular}{lcccrrrrrrrr}
  \hline
meta.id & file.nr & comparison.nr & subgroup.nr & z fixed & z random & z Copas & z regression & g fixed & g random & g Copas & g regression \\ 
  \hline
2009 & 2009 & 1 & 1 & 0.31 & 0.36 & 0.31 & 0.43 & 0.70 & 0.70 & 0.70 & 2.48 \\ 
  2068 & 2068 & 2 & 0 & 0.29 & 0.35 & 0.29 & 0.42 & 0.68 & 0.68 & 0.68 & 2.57 \\ 
  52528 & 52528 & 1 & 0 & -0.75 & -0.69 & -0.50 & -0.26 & -1.19 & -1.53 & 0.18 & -0.52 \\ 
  60546 & 60546 & 1 & 1 & 0.17 & 0.24 & 0.17 & 0.34 & 0.53 & 0.53 & 0.53 & 1.65 \\ 
  70389 & 70389 & 1 & 1 & -0.08 & -0.07 & 15.62 & -0.04 & -0.13 & -0.13 & -0.13 & -0.05 \\ 
  73769 & 73769 & 3 & 1 & -0.09 & 0.00 & 7148.96 & 0.02 & -0.01 & -0.12 & 0.01 & 0.04 \\ 
  79113 & 79113 & 2 & 0 & -0.38 & -0.38 & -0.38 & -0.48 & -0.93 & -0.93 & -2.00 & -3.47 \\ 
  90138 & 90138 & 3 & 0 & 0.30 & 0.80 & 0.30 & 0.53 & 0.72 & 0.71 & 0.71 & 2.16 \\ 
  97356 & 97356 & 2 & 0 & -0.06 & -0.33 & -0.06 & -0.11 & -0.42 & -0.35 & -1.58 & -1.82 \\ 
  98030 & 98030 & 1 & 0 & -0.09 & -0.07 & -0.09 & -0.04 & -0.41 & -0.41 & -1.50 & -2.79 \\ 
  101436 & 101436 & 1 & 5 & 0.54 & 0.62 & 0.80 & 0.90 & 1.21 & 1.21 & 1.21 & 2.74 \\ 
  118121 & 118121 & 4 & 1 & 0.25 & 0.23 & 47.73 & -0.03 & 0.44 & 0.44 & 0.44 & 0.14 \\ 
  119537 & 119537 & 3 & 0 & 0.07 & 0.15 & 0.07 & 0.29 & 0.50 & 0.50 & 1.43 & 1.81 \\ 
  119818 & 119818 & 3 & 3 & -0.25 & -0.25 & -0.20 & -0.04 & -0.50 & -0.54 & 28.44 & -0.03 \\ 
  146301 & 146301 & 1 & 0 & 0.14 & 0.26 & 472149.03 & 0.28 & 0.56 & 0.37 & 0.60 & 0.52 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Missing meta-analysis pooled treatment effect and adjusted treatment effects. Abbreviations are used for z-score (= z) and Hedges g (= g).} 
\label{missing.differences}
\end{table}
